---
title: "ACURA CSD Analysis V1.76"
author: "Russell Chan"
date: "8th April 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Set working directory
```{r working d}
setwd("C:/Users/Russell Chan/Dropbox/AA EXP 3 Paper 4 Analysis/Current Analysis")
```

##Packages
```{r Libraries, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(lme4)
library(effects)
library(lattice)
library(car)
library(ggplot2) 
library(knitr)
library(reshape2)
library(reshapeGUI)
library(dplyr)
library(forcats)
library(DHARMa)
library(Hmisc)
library(qpcR)
library(phia)
library(lsmeans)
library(emmeans)
library(multcomp)
library(plotly)
library(lmerTest)
library(optimx)
```

##Import dataset
```{r Import dataset and factors, paged.print=FALSE}
d.MU<-read.table("Pow_Data_DEC18_V3.4.CSV", sep = ",", header = T, stringsAsFactors = F)
```

#Factors
```{r Creating factors, message=FALSE, paged.print=FALSE}
#Create Factors
d.MU$ID <- factor(d.MU$ID)
d.MU$Group <- factor(d.MU$Group)
d.MU$RoI <- factor(d.MU$RoI, levels=c('F', 'C', 'P'))
d.MU$Session <- factor(d.MU$Session, levels=c('1', '2', '3'))
#d.MU$Timepoint <-as.numeric(d.MU$Timepoint, levels=c('1', '2', '3', '4', '5', '6', '7', '8', '9', '10'))
#d.MU$Timepoint <- factor(d.MU$Timepoint)
d.MU$muTheta <- as.numeric(d.MU$muTheta)
d.MU$muAlpha <- as.numeric(d.MU$muAlpha)
```


#Model_THETA_1: Random Intercepts: ID. Random Slopes: RoI. Keeping it maximal.
```{r ModelT1, paged.print=FALSE}
m.T1 <- lmer(muTheta ~ Group * Session * RoI  + (1 | ID), data=d.MU, REML =TRUE, control = lmerControl(optimizer ="Nelder_Mead"))
Anova(m.T1)
m.T1test <- as(m.T1,"lmerModLmerTest")
summary(m.T1test, ddf="Satterthwaite")
plot(m.T1test)
```

#Model_THETA_1.5: Theta Random Intercepts: ID. No Random Slopes. Minimum model.
```{r ModelT1.5, paged.print=FALSE}
m.T1.5 <- lmer(muTheta ~ Group * Session * RoI  + (1 + RoI | ID), data=d.MU, REML =TRUE, control = lmerControl(optimizer ="Nelder_Mead"))
Anova(m.T1.5)
m.T1.5test <- as(m.T1.5,"lmerModLmerTest")
summary(m.T1.5test, ddf="Satterthwaite")
plot(m.T1.5test)
```
#Posthocs on each of the interactions(group level) in the predictors:m.T1.5 <- This is right.
```{r Interaction on T predictors}
summary(glht(m.T1.5, emm(pairwise ~ Group | Session * RoI)))
```

#Interaction plot of predictors: m.T1.5
```{r Interaction Plots T, paged.print=FALSE}
emmip(m.T1.5, Group ~ Session | RoI)
plot(emmeans(m.T1.5, ~ Group | Session*RoI))
```

#Model_ALPHA_1: Random Intercepts: ID. Random Slopes: RoI. Maximal.
```{r ModelA1, paged.print=FALSE}
m.A1 <- lmer(muAlpha ~ Group * Session * RoI  + (1 | ID), data=d.MU, REML = TRUE, control = lmerControl(optimizer ="Nelder_Mead"))
Anova(m.A1)
m.A1test <- as(m.A1,"lmerModLmerTest")
summary(m.A1test, ddf="Satterthwaite")
plot(m.A1test)
```

#Model_ALPHA_1.5: Random Intercepts: ID. No Random Slopes.  Minimum model.
```{r ModelA1.5, paged.print=FALSE}
m.A1.5 <- lmer(muAlpha ~ Group * Session * RoI  + (1 + RoI | ID), data=d.MU, REML = TRUE, control = lmerControl(optimizer ="Nelder_Mead"))
Anova(m.A1.5)
m.A1.5test <- as(m.A1.5,"lmerModLmerTest")
summary(m.A1.5test, ddf="Satterthwaite")
plot(m.A1.5test)
```

#Posthocs on each of the interactions(group level) in the predictors:m.A1.5 <- This is right.
```{r Interaction on A predictors}
summary(glht(m.A1.5, emm(pairwise ~ Group | Session * RoI)))
```

#Interaction plot of predictors: m.A1.5
```{r Interaction A Plots, paged.print=FALSE}
emmip(m.A1.5, Group ~ Session | RoI)
plot(emmeans(m.A1.5, ~ Group | Session*RoI))
```

#Modelfit checking.
```{r AIC, paged.print=FALSE}
anova(m.T1, m.T1.5)
anova(m.A1, m.A1.5)
```

#All effects Model T1 and A1 modeling SESSIONS model here.
```{r All effects}
#Model T1 Effects
ae.m.T1 <- allEffects(m.T1)
ae.m.df.T1 <- as.data.frame(ae.m.T1[[1]])
#Ordering RoI
ae.m.df.T1$RoI <- factor(ae.m.df.T1$RoI, levels=c('F', 'C', 'P'))
#Ordering Session
ae.m.df.T1$Session <- as.character(ae.m.df.T1$Session)
ae.m.df.T1$Session <- as.numeric(ae.m.df.T1$Session)

#Model T1.5 Effects
ae.m.T1.5 <- allEffects(m.T1.5)
ae.m.df.T1.5 <- as.data.frame(ae.m.T1.5[[1]])
#Ordering RoI
ae.m.df.T1.5$RoI <- factor(ae.m.df.T1.5$RoI, levels=c('F', 'C', 'P'))
#Ordering Session
ae.m.df.T1.5$Session <- as.character(ae.m.df.T1.5$Session)
ae.m.df.T1.5$Session <- as.numeric(ae.m.df.T1.5$Session)

#Model A1 Effects
ae.m.A1 <- allEffects(m.A1)
ae.m.df.A1 <- as.data.frame(ae.m.A1[[1]])
#Ordering RoI
ae.m.df.A1$RoI <- factor(ae.m.df.A1$RoI, levels=c('F', 'C', 'P'))
#Ordering Session
ae.m.df.A1$Session <- as.character(ae.m.df.A1$Session)
ae.m.df.A1$Session <- as.numeric(ae.m.df.A1$Session)

#Model A1.5 Effects
ae.m.A1.5 <- allEffects(m.A1.5)
ae.m.df.A1.5 <- as.data.frame(ae.m.A1.5[[1]])
#Ordering RoI
ae.m.df.A1.5$RoI <- factor(ae.m.df.A1.5$RoI, levels=c('F', 'C', 'P'))
#Ordering Session
ae.m.df.A1.5$Session <- as.character(ae.m.df.A1.5$Session)
ae.m.df.A1.5$Session <- as.numeric(ae.m.df.A1.5$Session)
```

#RAW effects plots
```{r Plot just for general visualisation}
plot(ae.m.T1)
plot(ae.m.T1.5)
plot(ae.m.A1)
plot(ae.m.A1.5)
```

#Plotting models T1.5 & A1.5 (95% CIs). Since they are significantly better models 
```{r Plotting the models}
#Model T1.5 plot: with 95% CIs
ae.T1.5 <- ggplot(ae.m.df.T1.5, aes(x=Session,y=fit, color=Group))+
  geom_line() +
  geom_path(aes(x=Session, y=fit, color=Group)) +
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.1) +
  geom_point(aes(color = Group))+
  ylab("Mean Current Source Density (n.u.)")+
  scale_x_continuous(name="Session", breaks=c(1,2,3) , limits=c(0.75,3.25))+
  ggtitle("Theta M1.5: Group x Session x RoI")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  facet_grid(RoI~.)
plot(ae.T1.5)

#Model A1 plot: with 95% CIs
ae.A1.5 <- ggplot(ae.m.df.A1.5, aes(x=Session,y=fit, color=Group))+
  geom_line() +
  geom_path(aes(x=Session, y=fit, color=Group)) +
  geom_errorbar(aes(ymin=lower, ymax=upper), width=.1) +
  geom_point(aes(color = Group))+
  ylab("Mean Current Source Density (n.u.)")+
  scale_x_continuous(name="Session", breaks=c(1,2,3) , limits=c(0.75,3.25))+
  ggtitle("Alpha M1.5: Group x Session x RoI")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  facet_grid(RoI~.)
plot(ae.A1.5)
```

######################################################################################################
